### 2022-09-29 inst/Examples/Paper_results/Paper_results_1.Rmd
Revert back to something that was working

The data used is the NGRIP/GICC05 data set 'NGRIP_d18O_and_dust_5cm', downloaded from [Centre for Ice and Climate](iceandclimate.nbi.ku.dk) at the Niels Bohr Institute of the University of Copenhagen, Denmark, and the table of stadial-interstadial events presented by [Rasmussen et al. (2014)](https://www.sciencedirect.com/science/article/pii/S0277379114003485). These are included in the package and can be imported as follows. 
```{r bremla, eval=TRUE}
library(bremla)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")

age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
proxy = NGRIP_5cm$d18O
n=length(diff(age))

data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,proxy=proxy)
events=list(locations = events_rasmussen$depth,
            locations_unit="depth",degree=1)

plot(depth,proxy,xlab="Age (yb2k)",ylab=expression(paste(d^18,"O (permil)")),type="l",
     xlim=rev(range(depth)))+abline(v=events$locations,col="gray",lwd=0.7)
formula = dy~-1+depth2+proxy

nsims=3000

results = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE) ,
                print.progress=TRUE
                )

```

@@

```{r ls, eval=TRUE}
fit = results$fitting$LS$fit

{
  par(mfrow=c(2,1),mar=c(5,4,4,2)+0.1)
plot(results$data$depth,results$data$dy,type="l",xlab="Depth (m)",ylab="Layers per 5cm",main="(a) Least squares fit",xlim=rev(range(results$data$depth))) + lines(results$data$depth,fit$fitted.values,col="red")   
abline(v=events$locations,col="gray",lwd=0.8)
legend(1770,6.35,legend=c("Layer increments","Regression fit","Climate transitions"),
       col=c("black","red","gray"),lty=c(1,1,NA),cex=0.9,pch=c(NA,NA,"|"))
plot(results$data$depth,fit$residuals,type="l",xlab="Depth (m)",ylab="Residual errors per 5cm",main="(b) Least squares residuals",xlim=rev(range(results$data$depth)))
}
{
layout(mat=matrix(c(1,3,2,3),nrow=2))
  par(mar=c(5,3.5,4,2)+0.1)
hist(fit$residuals,xlab="Residual errors per 5cm",ylab="Density",main="(a) Histogram", col="orange")
{qqnorm(fit$residuals,main="(b) Q-Q Plot")
qqline(fit$residuals)}
acf(fit$residuals, lag.max = 20,main="(c) Autocorrelation function")
}
par(mfrow=c(1,1))
```

To compare the final age-depth uncertainties across the iid, AR(1) and AR(2) models run:
```{r iid_ar2, eval=TRUE}
resultsiid = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="iid"),
                control.sim=list(synchronized=FALSE) 
                )

resultsar2 = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar2"),
                control.sim=list(synchronized=FALSE) 
                )

gicc05 = results$original.chron$age[1+1:n]
{
plot(depth[1+1:n],resultsar2$simulation$summary$upper-gicc05,type="l",col="red", xlab="Depth (m)", ylab="Simulated time scale - GICC05 (years)",ylim=c(-260,260),xlim=rev(range(depth)), lwd=2)
lines(depth[1+1:n],results$simulation$summary$upper-gicc05,col="blue",lwd=2)
lines(depth[1+1:n],resultsiid$simulation$summary$upper-gicc05,col="black",lwd=2)
lines(depth[1+1:n],results$simulation$summary$mean-gicc05,col="gray",lwd=2)
abline(h=0,lty=3)
lines(depth[1+1:n],results$simulation$summary$lower-gicc05,col="blue",lwd=2)
lines(depth[1+1:n],resultsiid$simulation$summary$lower-gicc05,col="black",lwd=2)
lines(depth[1+1:n],resultsar2$simulation$summary$lower-gicc05,col="red",lwd=2)
legend(1640,275,legend=c("Mean","iid CI","AR(1) CI", "AR(2) CI"),
       col=c("gray","black","blue","red"),lty=c(1,1,1,1),cex=0.75)
}
```

@@

```{r biased, eval=TRUE}

results_biased = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE),
                control.bias=list(bias.model="uniform",nsims=nsims,
                                  biasparams = matrix(c(0.98,1.02,0.96,1.04),nrow=2)
                                  ),
                print.progress=TRUE
                )

{
  plot(depth[1+1:n],results_biased$biases$bias1$quant0.975-gicc05,type="l",col="blue",lty=2, xlab="depth", ylab="Simulated time scale - GICC05 (years)",xlim = rev(range(depth)), ylim = c(-2700,2700))
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.975-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], results$simulation$summary$upper-gicc05,col="blue",lty=1)
  abline(h=0,lty=3,col="gray")
  lines(depth[1+1:n], results$simulation$summary$lower-gicc05,col="blue",lty=1)
  lines(depth[1+1:n], results_biased$biases$bias1$quant0.025-gicc05,col="blue",lty=2)
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.025-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], NGRIP_5cm$MCE[1+1:n],col="black",lwd=2)
  legend(1660,2700,legend=c("MCE","Unbiased","2% bias rate", "4% bias rate"),
       col=c("black","blue","blue","blue"),lty=c(1,1,2,3),lwd=c(2,1,1,1),cex=0.65)
}

```

@@

```{r events_individual, eval=TRUE}

eventnumber=13 #number between 1 and 29. specifies which transition to consider

#load data window and specifics to transition
lowerints = which.index(event_intervals$depth_int_lower.m, depth[2:length(depth)])
upperints = which.index(event_intervals$depth_int_upper.m, depth[2:length(depth)])
depth.reference = event_intervals$NGRIP_depth_m[eventnumber]
age.reference = event_intervals$GICC_age.yb2k[eventnumber]
interval = lowerints[eventnumber]:upperints[eventnumber]

transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])

control.linramp=list(proxy=proxy,
                     interval=interval,
                     interval.unit="index",
                     depth.reference=event_intervals$NGRIP_depth_m[eventnumber]
                     )

results_event = linrampfitter(results,control.linramp)

control.transition_dating = list(label="Simulated transition")
results_event = events_depth_to_age(results_event,
                                    control.transition_dating=control.transition_dating)
{
  layout(mat=matrix(c(1,3,2,3),nrow=2))

  plot(depth[interval],proxy[interval],type="l",col="gray",
     main=paste0("(a) ",transitionlabel," linear ramp fit"),
     xlab="Depth (m)", ylab=paste(expression(delta^18,"O (permil)")),
     xlim = rev(range(depth[interval]))
     )
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$mean,lwd=1.5)
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$q0.025,lwd=1.5,col="red")
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$q0.975,lwd=1.5,col="red")
abline(v=depth.reference,lty=3,lwd=0.7,col="black")

ybottom = min(results_event$linramp$data$y)
ytop = min(results_event$linramp$linrampfit$q0.025)
margt0=results_event$linramp$param$t0$marg.t0
normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
ybottom = min(results_event$linramp$data$y)
ytop = min(results_event$linramp$linrampfit$q0.025)
margt1 = results_event$linramp$param$t1$marginal
normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)

plot(results_event$linramp$param$t0$marg.t0,type="l",xlab="Depth (m)",ylab="Density",
     main="(b) Marginal posterior of onset depth", 
     xlim=rev(range(depth.reference,results_event$linramp$param$t0$marg.t0[,1])))
abline(v=depth.reference,lty=3)
abline(v=results_event$linramp$param$t0$mean,lwd=1.5)
abline(v=results_event$linramp$param$t0$q0.025,col="gray")
abline(v=results_event$linramp$param$t0$q0.975,col="gray")

hist(results_event$event_dating$samples,main="(c) Histogram of onset age",
     xlab="Onset age (yr b2k)",col="orange",xlim=rev(range(results_event$event_dating$samples)), breaks=40)
abline(v=age.reference,lty=3)
abline(v=results_event$event_dating$mean,lwd=2)

par(mar=c(5,3.5,4,2)+0.1)
}

```

@@

```{r events_import, eval=TRUE}
library(readxl)
rasmussen_depths = event_intervals$NGRIP_depth_m
rasmussen_ages = event_intervals$GICC_age.yb2k #GISevents$`Age (a b2k)`

buizert_onsets = read_excel("inst/Examples/Paper_results/data/Buizert_onsets.xlsx",
                            col_types=c("text","numeric","numeric","numeric","numeric"))
buizert_depths = buizert_onsets$Depth; buizert_ages = buizert_onsets$Age
#buizert_depths[c(2:6,8:9,12:13,15:17,19:21)]
buizert_ages = buizert_ages[c(2:6,8:9,12:13,15:17,19:21)]

capron_onsets_NGRIP_d18O = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                           sheet="d18O",n_max=25)
capron_ages_NGRIP_d18O = capron_onsets_NGRIP_d18O$`t1 (50%)`

capron_onsets_NGRIP_dust = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                                sheet="Ca2+",n_max=24)
capron_ages_NGRIP_dust = capron_onsets_NGRIP_dust$`t1 (50%)`

capind = numeric(29); buiind = numeric(29)

capind = c(NA,2,3, 4,5,6,NA,NA,7,8,NA,9,10,11,NA,NA,NA,NA,NA,12,13,14,NA,NA,15,NA,NA,16,17)
buiind = c(NA,2,NA,3,4,6,NA,NA,8,9,NA,11,12,13,NA,NA,NA,NA,NA,15,16,17,NA,NA,19,NA,NA,20,21)
```

@@

```{r events_imputedust, eval=TRUE}
dust = NGRIP_5cm$logdust
library(zoo)
dust_filled = na.approx(dust) #Impute missing data using linear interpolation
logdust = log(dust_filled)

data2=data
data2$proxy = logdust
results_dust = bremla(formula,data2,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE) 
                )
```

@@

```{r events_all, evals=TRUE}
agesimmatrix_dust = matrix(NA,29,nsims)
agesimmatrix_d18O = matrix(NA,29,nsims)
depthlist_dust = c()
depthlist_d18O = c()
do.plot.rampfit = FALSE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,7,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,7,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")

# below is some fiddling with optimization parameters to improve the linear ramp fit for 
# some of the more challenging fits

steplengths = rep(0.005,29) 
steplengths[c(5,10)]=0.0001 #sometimes changing the steplength in the INLA optimization procedure can improve convergence (default is 0.005)
#compute.dust = rep(TRUE,29); compute.dust[c(8,27)]=FALSE #
#dtparams1 = rep(1,29); dtparams2 = rep(0.2,29) #prior-parameters for transition length
#t0params1 = rep(1,29); t0params2 = rep(0.2,29) #prior-parameters for transition onset
#dtparams1[10] = 20; dtparams2[10] = 0.1 #
#t0params1[10] = 120; t0params2[10] = 20

for(eventnumber in 1:29){
  if(eventnumber == 10){ #one of the transitions struggled to find good initial value 
    opt.params = c(40,NA,NA,NA) #for onset depth
    priorparams=NULL
  }else{
    opt.params = NULL
    priorparams=NULL
  }

@@

}

```

@@

}
par(mar=c(0,0,0,0));plot(-1,axes=FALSE,xlab="",ylab="",xlim=c(0,1),ylim=c(0,1))
legend(0,1,legend=c("d18O onset posterior","Ca2+ onset posterior",
                    "Rasmussen onset","Buizert onset",
                    "Capron d18O onset","Capron Ca2+ onset"),
       col=c("black","gray", "blue", "green", "red", "pink"),
       lty=c(1,1,1,1,1,1), cex=0.65,bty="n")

par(mfrow=c(1,1),mar=c(5,4,4,2)+0.1)
rownames=c()
for(i in 1:29){
  rownames=c(rownames,str_sub(event_intervals[i,2],str_locate(event_intervals[i,2],"GI-")[1]))
}

```

@@

```{r events_table, eval=TRUE}

colnames = c("d18O_mean","d18O_q0.025","d18O_q0.975",
             "Ca_mean","Ca_q0.025","Ca_q0.975")
depthresults = t(depthstats)[,2:7]
colnames(depthresults)=colnames
rownames(depthresults)=rownames

ageresults = t(agestats[2:7,])
colnames(ageresults)=colnames
rownames(ageresults)=rownames

```

>>>>

The data used is the NGRIP/GICC05 data set 'NGRIP_d18O_and_dust_5cm', downloaded from [Centre for Ice and Climate](iceandclimate.nbi.ku.dk) at the Niels Bohr Institute of the University of Copenhagen, Denmark, and the table of stadial-interstadial events presented by [Rasmussen et al. (2014)](https://www.sciencedirect.com/science/article/pii/S0277379114003485). These are included in the package and can be imported as follows. 
```{r bremla, eval=TRUE}
library(bremla)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")
age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
proxy = NGRIP_5cm$d18O
n=length(diff(age))
data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,proxy=proxy)
events=list(locations = events_rasmussen$depth,
            locations_unit="depth",degree=1)
plot(depth,proxy,xlab="Age (yb2k)",ylab=expression(paste(d^18,"O (permil)")),type="l",
     xlim=rev(range(depth)))+abline(v=events$locations,col="gray",lwd=0.7)
formula = dy~-1+depth2+proxy
nsims=3000
results = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE) ,
                print.progress=TRUE
                )
```

@@

```{r ls, eval=TRUE}
fit = results$fitting$LS$fit
{
  par(mfrow=c(2,1),mar=c(5,4,4,2)+0.1)
plot(results$data$depth,results$data$dy,type="l",xlab="Depth (m)",ylab="Layers per 5cm",main="(a) Least squares fit",xlim=rev(range(results$data$depth))) + lines(results$data$depth,fit$fitted.values,col="red")   
abline(v=events$locations,col="gray",lwd=0.8)
legend(1770,6.35,legend=c("Layer increments","Regression fit","Climate transitions"),
       col=c("black","red","gray"),lty=c(1,1,NA),cex=0.9,pch=c(NA,NA,"|"))
plot(results$data$depth,fit$residuals,type="l",xlab="Depth (m)",ylab="Residual errors per 5cm",main="(b) Least squares residuals",xlim=rev(range(results$data$depth)))
}
{
layout(mat=matrix(c(1,3,2,3),nrow=2))
  par(mar=c(5,3.5,4,2)+0.1)
hist(fit$residuals,xlab="Residual errors per 5cm",ylab="Density",main="(a) Histogram", col="orange")
{qqnorm(fit$residuals,main="(b) Q-Q Plot")
qqline(fit$residuals)}
acf(fit$residuals, lag.max = 20,main="(c) Autocorrelation function")
}
par(mfrow=c(1,1))
```

To compare the final age-depth uncertainties across the iid, AR(1) and AR(2) models run:
```{r iid_ar2, eval=TRUE}
resultsiid = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="iid"),
                control.sim=list(synchronized=FALSE) 
                )
resultsar2 = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar2"),
                control.sim=list(synchronized=FALSE) 
                )
gicc05 = results$original.chron$age[1+1:n]
{
plot(depth[1+1:n],resultsar2$simulation$summary$upper-gicc05,type="l",col="red", xlab="Depth (m)", ylab="Simulated time scale - GICC05 (years)",ylim=c(-260,260),xlim=rev(range(depth)), lwd=2)
lines(depth[1+1:n],results$simulation$summary$upper-gicc05,col="blue",lwd=2)
lines(depth[1+1:n],resultsiid$simulation$summary$upper-gicc05,col="black",lwd=2)
lines(depth[1+1:n],results$simulation$summary$mean-gicc05,col="gray",lwd=2)
abline(h=0,lty=3)
lines(depth[1+1:n],results$simulation$summary$lower-gicc05,col="blue",lwd=2)
lines(depth[1+1:n],resultsiid$simulation$summary$lower-gicc05,col="black",lwd=2)
lines(depth[1+1:n],resultsar2$simulation$summary$lower-gicc05,col="red",lwd=2)
legend(1640,275,legend=c("Mean","iid CI","AR(1) CI", "AR(2) CI"),
       col=c("gray","black","blue","red"),lty=c(1,1,1,1),cex=0.75)
}
```

@@

```{r biased, eval=TRUE}
results_biased = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE),
                control.bias=list(bias.model="uniform",nsims=nsims,
                                  biasparams = matrix(c(0.98,1.02,0.96,1.04),nrow=2)
                                  ),
                print.progress=TRUE
                )
{
  plot(depth[1+1:n],results_biased$biases$bias1$quant0.975-gicc05,type="l",col="blue",lty=2, xlab="depth", ylab="Simulated time scale - GICC05 (years)",xlim = rev(range(depth)), ylim = c(-2700,2700))
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.975-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], results$simulation$summary$upper-gicc05,col="blue",lty=1)
  abline(h=0,lty=3,col="gray")
  lines(depth[1+1:n], results$simulation$summary$lower-gicc05,col="blue",lty=1)
  lines(depth[1+1:n], results_biased$biases$bias1$quant0.025-gicc05,col="blue",lty=2)
  lines(depth[1+1:n], results_biased$biases$bias2$quant0.025-gicc05,col="blue",lty=3)
  lines(depth[1+1:n], NGRIP_5cm$MCE[1+1:n],col="black",lwd=2)
  legend(1660,2700,legend=c("MCE","Unbiased","2% bias rate", "4% bias rate"),
       col=c("black","blue","blue","blue"),lty=c(1,1,2,3),lwd=c(2,1,1,1),cex=0.65)
}
```

@@

```{r events_individual, eval=TRUE}
eventnumber=13 #number between 1 and 29. specifies which transition to consider
#load data window and specifics to transition
lowerints = which.index(event_intervals$depth_int_lower.m, depth[2:length(depth)])
upperints = which.index(event_intervals$depth_int_upper.m, depth[2:length(depth)])
depth.reference = event_intervals$NGRIP_depth_m[eventnumber]
age.reference = event_intervals$GICC_age.yb2k[eventnumber]
interval = lowerints[eventnumber]:upperints[eventnumber]
transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])
control.linramp=list(proxy=proxy,
                     interval=interval,
                     interval.unit="index",
                     depth.reference=event_intervals$NGRIP_depth_m[eventnumber]
                     )
results_event = linrampfitter(results,control.linramp)
control.transition_dating = list(label="Simulated transition")
results_event = events_depth_to_age(results_event,
                                    control.transition_dating=control.transition_dating)
{
  layout(mat=matrix(c(1,3,2,3),nrow=2))

  plot(depth[interval],proxy[interval],type="l",col="gray",
     main=paste0("(a) ",transitionlabel," linear ramp fit"),
     xlab="Depth (m)", ylab=paste(expression(delta^18,"O (permil)")),
     xlim = rev(range(depth[interval]))
     )
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$mean,lwd=1.5)
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$q0.025,lwd=1.5,col="red")
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$q0.975,lwd=1.5,col="red")
abline(v=depth.reference,lty=3,lwd=0.7,col="black")
ybottom = min(results_event$linramp$data$y)
ytop = min(results_event$linramp$linrampfit$q0.025)
margt0=results_event$linramp$param$t0$marg.t0
normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
ybottom = min(results_event$linramp$data$y)
ytop = min(results_event$linramp$linrampfit$q0.025)
margt1 = results_event$linramp$param$t1$marginal
normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)
plot(results_event$linramp$param$t0$marg.t0,type="l",xlab="Depth (m)",ylab="Density",
     main="(b) Marginal posterior of onset depth", 
     xlim=rev(range(depth.reference,results_event$linramp$param$t0$marg.t0[,1])))
abline(v=depth.reference,lty=3)
abline(v=results_event$linramp$param$t0$mean,lwd=1.5)
abline(v=results_event$linramp$param$t0$q0.025,col="gray")
abline(v=results_event$linramp$param$t0$q0.975,col="gray")
hist(results_event$event_dating$samples,main="(c) Histogram of onset age",
     xlab="Onset age (yr b2k)",col="orange",xlim=rev(range(results_event$event_dating$samples)), breaks=40)
abline(v=age.reference,lty=3)
abline(v=results_event$event_dating$mean,lwd=2)
par(mar=c(5,3.5,4,2)+0.1)
}
```

@@

```{r events_import, eval=TRUE}
library(readxl)
rasmussen_depths = event_intervals$NGRIP_depth_m
rasmussen_ages = event_intervals$GICC_age.yb2k #GISevents$`Age (a b2k)`
buizert_onsets = read_excel("inst/Examples/Paper_results/data/Buizert_onsets.xlsx",
                            col_types=c("text","numeric","numeric","numeric","numeric"))
buizert_depths = buizert_onsets$Depth; buizert_ages = buizert_onsets$Age
#buizert_depths[c(2:6,8:9,12:13,15:17,19:21)]
buizert_ages = buizert_ages[c(2:6,8:9,12:13,15:17,19:21)]
capron_onsets_NGRIP_d18O = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                           sheet="d18O",n_max=25)
capron_ages_NGRIP_d18O = capron_onsets_NGRIP_d18O$`t1 (50%)`
capron_onsets_NGRIP_dust = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                                sheet="Ca2+",n_max=24)
capron_ages_NGRIP_dust = capron_onsets_NGRIP_dust$`t1 (50%)`
capind = numeric(29); buiind = numeric(29)
capind = c(NA,2,3, 4,5,6,NA,NA,7,8,NA,9,10,11,NA,NA,NA,NA,NA,12,13,14,NA,NA,15,NA,NA,16,17)
buiind = c(NA,2,NA,3,4,6,NA,NA,8,9,NA,11,12,13,NA,NA,NA,NA,NA,15,16,17,NA,NA,19,NA,NA,20,21)
```

@@

```{r events_imputedust, eval=TRUE}
dust = NGRIP_5cm$logdust
library(zoo)
dust_filled = na.approx(dust) #Impute missing data using linear interpolation
logdust = log(dust_filled)
data2=data
data2$proxy = logdust
results_dust = bremla(formula,data2,reference.label="GICC05",
                nsims=nsims,
                events=events,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=FALSE) 
                )
```

@@

```{r events_all, evals=TRUE}
agesimmatrix_dust = matrix(NA,29,nsims)
agesimmatrix_d18O = matrix(NA,29,nsims)
depthlist_dust = c()
depthlist_d18O = c()
do.plot.rampfit = FALSE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,7,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,7,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
# below is some fiddling with optimization parameters to improve the linear ramp fit for 
# some of the more challenging fits
steplengths = rep(0.005,29) 
steplengths[c(5,10)]=0.0001 #sometimes changing the steplength in the INLA optimization procedure can improve convergence (default is 0.005)
#compute.dust = rep(TRUE,29); compute.dust[c(8,27)]=FALSE #
#dtparams1 = rep(1,29); dtparams2 = rep(0.2,29) #prior-parameters for transition length
#t0params1 = rep(1,29); t0params2 = rep(0.2,29) #prior-parameters for transition onset
#dtparams1[10] = 20; dtparams2[10] = 0.1 #
#t0params1[10] = 120; t0params2[10] = 20
for(eventnumber in 1:29){
  if(eventnumber == 10){ #one of the transitions struggled to find good initial value 
    opt.params = c(40,NA,NA,NA) #for onset depth
    priorparams=NULL
  }else{
    opt.params = NULL
    priorparams=NULL
  }

@@

}
```

@@

}
par(mar=c(0,0,0,0));plot(-1,axes=FALSE,xlab="",ylab="",xlim=c(0,1),ylim=c(0,1))
legend(0,1,legend=c("d18O onset posterior","Ca2+ onset posterior",
                    "Rasmussen onset","Buizert onset",
                    "Capron d18O onset","Capron Ca2+ onset"),
       col=c("black","gray", "blue", "green", "red", "pink"),
       lty=c(1,1,1,1,1,1), cex=0.65,bty="n")
par(mfrow=c(1,1),mar=c(5,4,4,2)+0.1)
rownames=c()
for(i in 1:29){
  rownames=c(rownames,str_sub(event_intervals[i,2],str_locate(event_intervals[i,2],"GI-")[1]))
}
```

@@

```{r events_table, eval=TRUE}
colnames = c("d18O_mean","d18O_q0.025","d18O_q0.975",
             "Ca_mean","Ca_q0.025","Ca_q0.975")
depthresults = t(depthstats)[,2:7]
colnames(depthresults)=colnames
rownames(depthresults)=rownames
ageresults = t(agestats[2:7,])
colnames(ageresults)=colnames
rownames(ageresults)=rownames
```
